### 2014-03-15 src/methodology.Rnw
Fix the spaces after pit ops

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \pitin, \pitm, \pitcb, \pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \pitnc, \pitvmc, \pitnvmc, \pitm, \pitic, \pitemv. 
\subsubsection{Criteria IV}
Namin et al. used \pitin, \pitm, \piti, \pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
\subsubsection{Criteria V}
For this criteria, we utilized the approach suggested by
Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
are discarded at each step.

\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \pitvmc, \pitnvmc, \pitcc, \pitemv, and \pitri for
simple statements, and using \pitrc for control structures, which
replaced the boolean condition with false, resulting in removal of the
block of statements. The operator for return values was modeled using
\pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \pitdc,
which replaced the boolean condition with true, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However, as seen in Figure~\ref{fig:op},
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable. An interesting point is that using this
procedure statement deletion is no longer a simple mutation and
qualifies as a higher order mutation operator. In fact, the procedure
we outlined can be used in general to judge the effectiveness of a
higher order operator from the results of the first order mutation
operators that together compose the higher order mutant.

>>>>

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \Pitnc, \Pitvmc, \Pitnvmc, \Pitm, \Pitic, \Pitemv. 
\subsubsection{Criteria IV}
Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
\subsubsection{Criteria V}
For this criteria, we utilized the approach suggested by
Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
are discarded at each step.

\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri for
simple statements, and using \pitrc for control structures, which
replaced the boolean condition with false, resulting in removal of the
block of statements. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with true, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However, as seen in Figure~\ref{fig:op},
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable. An interesting point is that using this
procedure statement deletion is no longer a simple mutation and
qualifies as a higher order mutation operator. In fact, the procedure
we outlined can be used in general to judge the effectiveness of a
higher order operator from the results of the first order mutation
operators that together compose the higher order mutant.
